Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1)

### 2014-03-28 WSSSPE1_report/WSSSPE1_summary_report.tex
small changes

We classify software developed with a potentially wider audience and general
purpose usage in mind as Utility software. In the context of research, a
utility software could be defined as general purpose system applicable to one
or many generic tasks and/or enabling other software to run by providing a
suitable environment. Utility software typically do not address a fundamental
research challenge in a given scientific domain. Examples are collaborative
development frameworks such as \emph{GitHub} and \emph{Bitbucket}, distributed
and workflow computing frameworks such as \emph{Galaxy}, \emph{Swift},
\emph{Globus} and \emph{VisTrails}, and visualization frameworks such as
\emph{VisIT}.

@@

%Summary of above discussed cases: lessons, trends, commonalities, is there an ideal sustainability scenario?
In order to investigate the much discussed issue of career paths for developers
of scientific software, we conducted a small survey of the use-cases discussed
above with respect to the current status of its core developers. We looked at
the workshop submissions and the original cited papers for the respective
software. We looked at the webpages and source codes of the earliest versions
where available to find the original authors. we find that in a majority of
scientific software more than one original developers are still around, in some
cases for more than 10 years. Whereas, in the case of utility software
projects, it appears that at least one original developer is still around often
in a part-time role. In other cases, it appears that the original developers
have went on to assume a larger role, again with the same project.

>>>>

We classify software developed with a potentially wider audience and general
purpose usage in mind as Utility software. In the context of research, a
utility software could be defined as general purpose system applicable to one
or many generic tasks and/or enabling other software to run by providing a
suitable environment. Utility software typically do not address a fundamental
research challenge in a given scientific domain. Examples are collaborative
development frameworks such as \emph{GitHub} and \emph{Bitbucket}, distributed
and workflow and generic computing frameworks such as \emph{Galaxy},
\emph{nanoHUB}, \emph{SimGrid}, \emph{Swift}, \emph{Globus} and \emph{VisTrails}, and
visualization frameworks such as \emph{VisIT}.

@@

%Summary of above discussed cases: lessons, trends, commonalities, is there an ideal sustainability scenario?
In order to investigate the much discussed issue of career paths for developers
of scientific software, we conducted a small survey of the use-cases discussed
above with respect to the current status of its core developers. We looked at
the workshop submissions and the original cited papers for the respective
software. We looked at the webpages and source codes of the earliest versions
where available to find the original authors. we find that in a majority of
scientific software more than one original developers are still around, in some
cases for more than 10 years, (eg. \emph{R/qtl}). Whereas, in the case of
utility software projects, it appears that at least one original developer is
still around often in a part-time role. In other cases, it appears that the
original developers have went on to assume a larger role, again with the same
project.
